The effect of genetic linkage on island endemics richness

### 2018-08-20 paper/draft.tex
disc: temporal dynamics of radiations FL vs NL

\section{Discussion}
%Assortative mating

>>>>

\section{Discussion}
The fact that low-linkage (single) species speciated in general faster than their high-linkage counterparts
is in line with expectations given their higher potential for fast evolutionary response [as exemplified REFS].
What did come as a surprise, however was that, over time, high linkage lineages surpassed low linkage lineages
in the number of emerging species.

%Assortative mating
